|

### 2025-12-03 manuscript/pre_print.qmd
Preprint ready for submission

@@

keywords: Polycystic ovary syndrome, PCOS, resting energy expenditure, REE, basal metabolic rate, BMR

@@

Studies were carried out in multiple countries: Brazil (k = `r filter(countries, country == "Brazil")$n`) ,and USA (k = `r filter(countries, country == "USA")$n` studies), Australia, Cameroon, Canada, Italy, Sweden, Turkey, UK (all k = 1 study). The four studies with noted reporting errors were carried out in Greece. A total of 11 studies used the Rotterdam criteria (or a modified version there of) for diagnosing PCOS [@robinsonPostprandialThermogenesisReduced1992; @brunerEffectsExerciseNutritional2006; @moranShorttermMealReplacements2006; @cosarRestingMetabolicRate2008; @graffDietaryGlycemicIndex2013; @pohlmeierEffectLowstarchLowdairy2014; @dohRelationshipAdiposityInsulin2016; @larssonDietaryIntakeResting2016; @graffSaturatedFatIntake2017; @rodriguesLowValidityPredictive2018; @tosiInsulinMediatedSubstrateUse2021]. One study used the 1990 National Institutes of Health criteria [@broskeyAssessingEnergyRequirements2017], and two studies [@segalRestingMetabolicRate1990; @robinsonPostprandialThermogenesisReduced1992] diagnosed PCOS via the presence of oligomenorrhea or amenorrheaammenorrhea alongside additional criteria including plasma androgen levels, hirsutism or polycystic ovaries on ultrasound scanning. All but one study [@broskeyAssessingEnergyRequirements2017], which used doubly labelled water, measured REE using indirect calorimetry. The specific devices reported by these studies are included in the online supplementary materials (see [Descriptives Table](https://html-preview.github.io/?url=https://github.com/jamessteeleii/pcos_ree_meta/raw/refs/heads/main/tables/descriptives_table.html)). We originally considered in our pre-registration that, given sufficient data, we would compare sub groups of women with PCOS who did and did not have accompanying insulin resistance. However, based on the metabolic health variables reported in studies with this information (see [Descriptives Table](https://html-preview.github.io/?url=https://github.com/jamessteeleii/pcos_ree_meta/raw/refs/heads/main/tables/descriptives_table.html)) and, where available, considering primary criteria of either homeostatic model assessment of insulin resistance (HOMA-IR) $\geq2.5$ or secondary criteria including fasting insulin $>12\mu \textrm{U/mL}$ or fasting glucose $\geq100\textrm{mg/dL}$, all groups of women with PCOS in the included studies would be considered to have insulin resistance. Mean age of women with PCOS in these studies ranged from `r summary_descriptives$min_age[2]` to `r summary_descriptives$max_age[2]` which was similar to the control women without PCOS ranging from `r summary_descriptives$min_age[1]` to `r summary_descriptives$max_age[1]`. Across those studies where BMI was reported or it was possible to estimate the mean BMI of women with PCOS ranged from `r summary_descriptives$min_bmi[2]` to `r summary_descriptives$max_bmi[2]` was typically greater than women without PCOS which ranged `r summary_descriptives$min_bmi[1]` to `r summary_descriptives$max_bmi[1]`.

@@

# Financial Disclosures/Conflicts of Interest
Leigh Peele is employed by MacroFactor, a nutrition-tracking app. Gregory Nuckols is co-owner of MacroFactor. Hannah Cabré was supported by the National Institute of Diabetes and Digestive and Kidney Diseases of the National Institutes of Health under Award Number T32DK064584. Alyssa Olenick provides fitness coaching and scientific consulting under ALYSSA OLENICK LLC. She receives compensation from scientific consulting, speaking engagments, affiliated social media partnerships, and book publishing. James Steele provides research consultancy through his company Steele Research Limited, is contracted currently by MacroFactor and Kieser Australia through Steele Research Limited, and has also received travel expenses and honoraria for speaking from fit20 International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health or any other funding agencies or institutions noted above. The authors declare no other conflicts of interest related to the submitted work

>>>>

        \usepackage{etoolbox}
        \AtEndEnvironment{abstract}{\noindent\textbf{Keywords:} \KeywordList \par}

@@

keywords: Polycystic ovary syndrome, Energy Metabolism, Resting Metabolic Rate, Basal Metabolism

@@

Studies were carried out in multiple countries: Brazil (k = `r filter(countries, country == "Brazil")$n`) ,and USA (k = `r filter(countries, country == "USA")$n` studies), Australia, Cameroon, Canada, Italy, Sweden, Turkey, UK (all k = 1 study). The four studies with noted reporting errors were carried out in Greece. A total of 11 studies used the Rotterdam criteria (or a modified version there of) for diagnosing PCOS [@robinsonPostprandialThermogenesisReduced1992; @brunerEffectsExerciseNutritional2006; @moranShorttermMealReplacements2006; @cosarRestingMetabolicRate2008; @graffDietaryGlycemicIndex2013; @pohlmeierEffectLowstarchLowdairy2014; @dohRelationshipAdiposityInsulin2016; @larssonDietaryIntakeResting2016; @graffSaturatedFatIntake2017; @rodriguesLowValidityPredictive2018; @tosiInsulinMediatedSubstrateUse2021]. One study used the 1990 National Institutes of Health criteria [@broskeyAssessingEnergyRequirements2017], and two studies [@segalRestingMetabolicRate1990; @robinsonPostprandialThermogenesisReduced1992] diagnosed PCOS via the presence of oligomenorrhea or amenorrhea alongside additional criteria including plasma androgen levels, hirsutism or polycystic ovaries on ultrasound scanning. All but one study [@broskeyAssessingEnergyRequirements2017], which used doubly labelled water, measured REE using indirect calorimetry. The specific devices reported by these studies are included in the online supplementary materials (see [Descriptives Table](https://html-preview.github.io/?url=https://github.com/jamessteeleii/pcos_ree_meta/raw/refs/heads/main/tables/descriptives_table.html)). We originally considered in our pre-registration that, given sufficient data, we would compare sub groups of women with PCOS who did and did not have accompanying insulin resistance. However, based on the metabolic health variables reported in studies with this information (see [Descriptives Table](https://html-preview.github.io/?url=https://github.com/jamessteeleii/pcos_ree_meta/raw/refs/heads/main/tables/descriptives_table.html)) and, where available, considering primary criteria of either homeostatic model assessment of insulin resistance (HOMA-IR) $\geq2.5$ or secondary criteria including fasting insulin $>12\mu \textrm{U/mL}$ or fasting glucose $\geq100\textrm{mg/dL}$, all groups of women with PCOS in the included studies would be considered to have insulin resistance. Mean age of women with PCOS in these studies ranged from `r summary_descriptives$min_age[2]` to `r summary_descriptives$max_age[2]` which was similar to the control women without PCOS ranging from `r summary_descriptives$min_age[1]` to `r summary_descriptives$max_age[1]`. Across those studies where BMI was reported or it was possible to estimate the mean BMI of women with PCOS ranged from `r summary_descriptives$min_bmi[2]` to `r summary_descriptives$max_bmi[2]` was typically greater than women without PCOS which ranged `r summary_descriptives$min_bmi[1]` to `r summary_descriptives$max_bmi[1]`.

@@

# Financial Disclosures/Conflicts of Interest
Richard Kirwan provides nutrition consultancy through his company Be More Nutrition. Leigh Peele is employed by MacroFactor, a nutrition-tracking app. Gregory Nuckols is co-owner of MacroFactor. Georgia Kohlhoff provides nutrition consultancy through her company Flourishing Health. Hannah Cabré was supported by the National Institute of Diabetes and Digestive and Kidney Diseases of the National Institutes of Health under Award Number T32DK064584. Alyssa Olenick provides fitness coaching and scientific consulting under ALYSSA OLENICK LLC. She receives compensation from scientific consulting, speaking engagments, affiliated social media partnerships, and book publishing. James Steele provides research consultancy through his company Steele Research Limited, is contracted currently by MacroFactor and Kieser Australia through Steele Research Limited, and has also received travel expenses and honoraria for speaking from fit20 International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health or any other funding agencies or institutions noted above. The authors declare no other conflicts of interest related to the submitted work.
